todo: think about good title

### 2018-12-20 documentation/paper.tex
added scores of the bots competing against each other
some calculations and adding them into the documentation

@@

>>>>

\begin{figure}
\begin{tabular}{c|ccccccc}
vs. & 
\texttt{ Axji-0-2 } &
\texttt{ COM\_11 } &
\texttt{ GintonicV9 } &
\texttt{ Hypo14 } &
\texttt{ reduced } &
\texttt{ Union } &
\texttt{ trainer } \\
\hline
\texttt{ Axji-0-2 } & - & 0 & 0 & 4 & 0 & 0 & 10 \\
\texttt{ COM\_11 } & 21 & - & 9 & 19 & 6 & 16 & 20 \\
\texttt{ GintonicV9 } & 21 & 12 & - & 19 & 6 & 16 & 20 \\
\texttt{ Hypo14 } & 17 & 2 & 2 & - & 2 & 5 & 15 \\
\texttt{ reduced } & 21 & 19 & 15 & 19 & - & 19 & 21 \\
\texttt{ Union } & 21 & 14 & 5 & 16 & 2 & - & 20 \\
\texttt{ trainer } & 11 & 0 & 1 & 6 & 0 & 1 & -
\end{tabular}
\caption{scores of bots competing against each other}
\end{figure}

@@

\section{Self adapt 1}

\begin{figure}[H]
\center
\begin{tabular}{ccc}
\texttt{reduced} & \texttt{com\_11} & \texttt{gintonicV9} \\
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_reduced.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_com_11.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_gintonicV9.png} \\
\texttt{hyp014} & \texttt{Union} & \texttt{trainer} \\
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_hyp014.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_Union.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_trainer.png}
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum.}
\label{fig:self_adapt_1}
\end{figure}

\begin{figure}[H]
\center
\begin{tabular}{ccc}
\texttt{reduced\_5t} & \texttt{com\_11\_5t} & \texttt{gintonicV9\_5t} \\
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_reduced_5t.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_com_11_5t.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_gintonicV9_5t.png} \\
\texttt{hyp014\_5t} & \texttt{Union\_5t} & \texttt{trainer\_5t} \\
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_hyp014_5t.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_Union_5t.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_trainer_5t.png}
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum.}
\label{fig:self_adapt_1_5t}
\end{figure}

\section{Self adapt 2}

Parameter tuning may be needed.

\begin{figure}[H]
\center
\begin{tabular}{ccc}
\texttt{reduced} & \texttt{com\_11} & \texttt{gintonicV9} \\
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_reduced.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_com_11.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_gintonicV9.png} \\
\texttt{hyp014} & \texttt{Union} & \texttt{trainer} \\
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_hyp014.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_Union.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_trainer.png}
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum.}
\label{fig:self_adapt_2}
\end{figure}

\begin{figure}[H]
\center
\begin{tabular}{ccc}
\texttt{reduced\_5t} & \texttt{com\_11\_5t} & \texttt{gintonicV9\_5t} \\
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_reduced_5t.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_com_11_5t.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_gintonicV9_5t.png} \\
\texttt{hyp014\_5t} & \texttt{Union\_5t} & \texttt{trainer\_5t} \\
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_hyp014_5t.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_Union_5t.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_trainer_5t.png}
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum.}
\label{fig:self_adapt_2_5t}
\end{figure}
